### 2019-04-24 sections/intuition.tex
correct spelling in intuition
convert back to two column layout
rename main tex file to main
use paragraph instead of subsubsection*

% !TEX root=../icfp2019.tex

@@

\subsection{Tasks model collaboration}
%NOTE: Heb toch maar deze kop toegevoegd, onderstaande gaat er duidelijk over, en de sprong van het voorbeeld naar "Tasks are reusable" is anders abrupt!

@@

\subsection{Tasks are reusable}

@@

\subsection{Tasks are driven by user input}

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneously to each if those events.

@@

\subsection{Tasks can be observed}

@@

\subsection{Tasks are never done}

@@

\subsection{Tasks can share information}

@@

\subsection{Tasks are predictable}

@@

\subsection{Recap}

Collaboration in the real world consists of three aspects: communication, concurrency, and synchronisation.
These aspects are reflected in \TOP on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.

By focussing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate distributed, multi-user applications to support such workflows.

>>>>

% !TEX root=../main.tex

@@

\paragraph{Tasks model collaboration}
%NOTE: Heb toch maar deze kop toegevoegd, onderstaande gaat er duidelijk over, en de sprong van het voorbeeld naar "Tasks are reusable" is anders abrupt!

@@

\paragraph{Tasks are reusable}

@@

\paragraph{Tasks are driven by user input}

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneously to each of those events.

@@

\paragraph{Tasks can be observed}

@@

\paragraph{Tasks are never done}

@@

\paragraph{Tasks can share information}

@@

\paragraph{Tasks are predictable}

@@

\paragraph{Recap}

Collaboration in the real world consists of three aspects: communication, concurrency, and synchronisation.
These aspects are reflected in \TOP on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.
By focussing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate multi-user applications to support such workflows.
